Bringing the Power of eBPF to Open vSwitch

### 2018-11-04 paper.tex
shorten the conference string
fix afxdp tx operation description
fix typo, move figure a little right

+-----------------------+
|    Network Stack      |
+---------^-------------+
          |
+---------|-------------+
| Traffic Control (TC)  | --> eBPF TC hook
+---------^-------------+
          |
+---------|-------------+
|     Driver (XDP)      | --> eBPF XDP hook
+---------^-------------+
          |
+---------|-------------+
|     Network card      |
+---------^-------------+
          |
          | packets

\end{verbatim}
}
\vspace{-1.0em}
\caption{eBPF program hook points in the Linux kernel.}
\label{ebpf-hook}
\vspace{-1.0em}
\end{figure}

@@

For example, to receive packets from XSK, firstly, the userspace program firstly
pushes a set of descriptors pointing to empty packet buffer into the Fill ring.
When a packet
arrives, kernel pops descriptors from the Fill ring, fills in the data into the
memory chunks pointed by the descriptors, and pushes the descriptors back to
the Rx ring.
The userspace program then checks the Rx ring, fetches the packet data from the
descriptors, and refills the empty buffer back to the Fill ring structure, so
that kernel can fill in new incoming packets later on.
For sending packets, the userspace program pushes a set of descriptors that
point to the packet buffers to the Tx ring, then issues sendmsg() system call.
Kernel consumes packet buffers asscoaited with the Tx ring, and pushes
transmitted descriptors to the Tx ring.
The userspace program then checks the Completion ring to determine whether the
packets have been sent.
In summary, XSK users need to properly program following four rings:
\begin{itemize}
\item Fill ring: for users to fill umem addresses to kernel for receiving packets.
\item Rx ring: for users to access received packets.
\item Tx ring: for users to place packets needed to be sent.
\item Completion ring: for users to check if packets are sent.
\end{itemize}
Unlike AF\_PACKET which is bound to entire netdev, the binding of XSK is more
fine-grained. XSK is bound to a specific queue on a device, so only the
traffic sent to the queue shows up in the XSK.

@@

Initially, assume ovs-vswitchd receives four packets from eth1's XSK.
To send packets to eth2 using eth2's XSK, ovs-vswitchd first gets four packet buffers,
\{4, 5, 6, 7\} from eth2's umempool and copies the packet data from eth1's umem
to eth2's umem at \{4, 5, 6, 7\}.  Later on, TX descriptors for the four packets are
created and placed into eth2's Tx ring (step 2).
At step 3, sendmsg syscall is issued to signal the kernel to start the transmission.
As the send msg syscall in XSK is asynchronous, ovs-vswitchd needs to poll
the COMPLETION ring to make sure that these four packets have been sent out
(step 4).
Once the four packets' descriptors show up at the COMPLETION ring, at step 5,
ovs-vswitchd recycles their umem elements back to eth2's umempool.
The original four packet buffers from eth1 are recycled back to eth1's
umempool as well.

>>>>

\begin{figure}
{\scriptsize
\begin{verbatim}
            +-----------------------+
            |    Network Stack      |
            +---------^-------------+
                      |
            +---------|-------------+
            | Traffic Control (TC)  | --> eBPF TC hook
            +---------^-------------+
                      |
            +---------|-------------+
            |     Driver (XDP)      | --> eBPF XDP hook
            +---------^-------------+
                      |
            +---------|-------------+
            |     Network card      |
            +---------^-------------+
                      |
                      | packets
\end{verbatim}
}
\vspace{-1.0em}
\caption{eBPF program hook points in the Linux kernel.}
\label{ebpf-hook}
\vspace{-1.0em}
\end{figure}

@@

For example, to receive packets from XSK, firstly, the userspace program firstly
pushes a set of descriptors pointing to empty packet buffer into the Fill ring.
When a packet
arrives, kernel pops descriptors from the Fill ring, fills in the data into the
memory chunks pointed by the descriptors, and pushes the descriptors back to
the Rx ring.
The userspace program then checks the Rx ring, fetches the packet data from the
descriptors, and refills the empty buffer back to the Fill ring structure, so
that kernel can fill in new incoming packets later on.
For sending packets, the userspace program pushes a set of descriptors that
point to the packet buffers to the Tx ring, then issues sendmsg() system call.
Kernel consumes packet buffers asscoaited with the Tx ring, and pushes
transmitted descriptors to the Completion ring.
The userspace program then checks the Completion ring to determine whether the
packets have been sent.
In summary, XSK users need to properly program following four rings:
\begin{itemize}
\item Fill ring: for users to fill umem addresses to kernel for receiving packets.
\item Rx ring: for users to access received packets.
\item Tx ring: for users to place packets needed to be sent.
\item Completion ring: for users to check if packets are sent.
\end{itemize}
Unlike AF\_PACKET which is bound to entire netdev, the binding of XSK is more
fine-grained. XSK is bound to a specific queue on a device, so only the
traffic sent to the queue shows up in the XSK.

@@

Initially, assume ovs-vswitchd receives four packets from eth1's XSK.
To send packets to eth2 using eth2's XSK, ovs-vswitchd first gets four packet buffers,
\{4, 5, 6, 7\} from eth2's umempool and copies the packet data from eth1's umem
to eth2's umem at \{4, 5, 6, 7\}.  Later on, TX descriptors for the four packets are
created and placed into eth2's Tx ring (step 2).
At step 3, sendmsg syscall is issued to signal the kernel to start the transmission.
As the sendmsg syscall in XSK is asynchronous, ovs-vswitchd needs to poll
the COMPLETION ring to make sure that these four packets have been sent out
(step 4).
Once the four packets' descriptors show up at the COMPLETION ring, at step 5,
ovs-vswitchd recycles their umem elements back to eth2's umempool.
The original four packet buffers from eth1 are recycled back to eth1's
umempool as well.
